The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
Add fig 1
Add figure references

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_1.png}
  \caption{
    Hypothesis 1: we expect the error made be correlated to the number 
    of species created by the multiple-birth process over the total number 
    of species created
  }
  \label{fig_h_1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_7.png}
  \caption{
    Hypothesis 7: there is no difference in inference errors if the MBD process
    generates many species in many modest MB events or few intense MB events
  }
  \label{fig_h_7}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_2.png}
  \caption{
    Hypothesis 2: the effect of extinction rates is neutral
  }
  \label{fig_h_2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_3.png}
  \caption{
    Hypothesis 3: the timing of a multiple birth event has no effect.
  }
  \label{fig_h_3}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_5.png}
  \caption{
    Hypothesis 5: the number of taxa does not
    have an effect on the error being made
  }
  \label{fig_h_5}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_6.png}
  \caption{
    Hypothesis 6: for a higher number of taxa 
    the variance in the error decreases
  }
  \label{fig_h_6}
\end{figure}

@@

\item To investigate the effect of $s$ on $e$, we simulate phylogenies
for different values of $s$ spread equally from zero (no multiple-birth
event, thus a BD model) to one (species are created only from multiple-birth
events) and three intermediate values of 0.25, 0.5 and 0.75.

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_4.png}
  \caption{
    Hypothesis 4: compared to the MBD trees, 
    the error will be less in the BD twin tree
  }
  \label{fig_h_4}
\end{figure}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r c l}
    \hline
    Symbol                & Expectation & Figure \\
    \hline
    \hline
    $\mathcal{H}_1$       & For a higher $s$, $e$ will increase monotonously & 1 \\
    $\mathcal{H}_2$       & Extinction rates have no effect on $e$ & 2 \\
    $\mathcal{H}_3$       & The timing of multiple-birth events has no effect on $e$ & 3 \\
    $\mathcal{H}_4$       & An MBD tree will have a higher $e$ than its twin BD counterpart & 4 \\
    $\mathcal{H}_5$       & The number of taxa has no effect on $e$ & 5 \\
    $\mathcal{H}_6$       & A higher number of taxa decreases the variance in $e$ & 6 \\
    $\mathcal{H}_7$       & The MBD regime has no effect on $e$ & 7 \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:hypotheses}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_1.png}
  \caption{
    Hypothesis 1: we expect the error made be correlated to the number 
    of species created by the multiple-birth process over the total number 
    of species created
  }
  \label{fig:h_1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_7.png}
  \caption{
    Hypothesis 7: there is no difference in inference errors if the MBD process
    generates many species in many modest MB events or few intense MB events
  }
  \label{fig:h_7}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_2.png}
  \caption{
    Hypothesis 2: the effect of extinction rates is neutral
  }
  \label{fig:h_2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_3.png}
  \caption{
    Hypothesis 3: the timing of a multiple birth event has no effect.
  }
  \label{fig:h_3}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_5.png}
  \caption{
    Hypothesis 5: the number of taxa does not
    have an effect on the error being made
  }
  \label{fig:h_5}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_6.png}
  \caption{
    Hypothesis 6: for a higher number of taxa 
    the variance in the error decreases
  }
  \label{fig:h_6}
\end{figure}

@@

\item To investigate the effect of $s$ on $e$, we simulate phylogenies
for different values of $s$ spread equally from zero (no multiple-birth
event, thus a BD model) to one (species are created only from multiple-birth
events) and three intermediate values of 0.25, 0.5 and 0.75. Aggregating all
components of $s$, we show the effect of $s$ on $e$ in figure 1.

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_4.png}
  \caption{
    Hypothesis 4: compared to the MBD trees, 
    the error will be less in the BD twin tree
  }
  \label{fig:h_4}
\end{figure}

@@

\item We expected the effect of $s$ on $e$ to be monotonously increasing
function (figure \ref{fig:h_1}). Figure \ref{fig:1} shows the effect 
measured in this experiment.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_1.png}
  \caption{
    The effect of s on e
  }
  \label{fig:1}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r c c c}
    \hline
    Symbol                & Expectation & Expected figure & Measured figure \\
    \hline
    \hline
    $\mathcal{H}_1$       & For a higher $s$, $e$ will increase monotonously & \ref{fig:h_1} & \ref{fig:1} \\
    $\mathcal{H}_2$       & Extinction rates have no effect on $e$ & \ref{fig:h_2} & Not yet \\
    $\mathcal{H}_3$       & The timing of multiple-birth events has no effect on $e$ & \ref{fig:h_3} & Not yet \\
    $\mathcal{H}_4$       & An MBD tree will have a higher $e$ than its twin BD counterpart & \ref{fig:h_4} & Not yet \\
    $\mathcal{H}_5$       & The number of taxa has no effect on $e$ & \ref{fig:h_5} & Not yet \\
    $\mathcal{H}_6$       & A higher number of taxa decreases the variance in $e$ & \ref{fig:h_6} & Not yet \\
    $\mathcal{H}_7$       & The MBD regime has no effect on $e$ & \ref{fig:h_7} & Not yet \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:hypotheses}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
